Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-19 paper/gen-graph-connected-heatmap.tex
Muck around with the graphs a bit, add some FC
More FC data
More gratuitous mucking around with the figures

%% Thu 07 Apr 2016 11:12:14 BST

@@

\node[gp node center] at (8.574,1.427) {MAC Both Runtime (ms)};

@@

  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ff9576ff9f7dff9f7dffffffffac88ff9f7d%
  ffffffff9f7dffac88ffffffff8c72ff8c72ffac88ffac88ffac88ff9f7dff846eff846efd6561fa5e5ffe6862ff7e6c%
  fe6862f85a5df7585df4505aef4457f04557e73952df2f4ee2324fd9284bd62449d42148d21f47d21f47cf1d44cd1b43%
  cc1b43d11e46d21f47cc1b43c7173ed01e46ca1940cd1c43cf1d45ce1c44d52349d42248dc2c4cda2a4cde2d4dd22047%
  d42248d8264ad7254ad7264aa00319ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%

@@

  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
  ffac88ff9f7dffffffff9f7dffffffffac88ff9f7dff9f7dffac88ffac88ffac88ff8c72ff6f65ff9f7dffac88ffac88%
  ff9f7dff8c72ff9f7dff7e6cff9576ff9576ffffffff9f7dff9f7dffffffffac88ffac88ffac88ffffffff9f7dff9f7d%
  ff9f7dffac88ffac88ff9f7dffac88ffffffffffffffffffffac88e1314fffffffffffffffffffffffffffffffffffff%

@@

  ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88%
  ffffffffffffff9576ffffffff9576ffffffffac88ffffffffffffff9576ffac88ffac88ff9576ff846eff9576ff9f7d%
  ffac88ff8c72ffffffffac88ff9576ff9576ff846eff846eff846eff7869ff7e6cff7869ff7e6cff846eff9576ff9f7d%
  ffac88ff846effffffff9f7dff9576ffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffe2324fffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
  ffffffffffffffffffffffffffffffffffffffac88ff8c72ffffffff9f7dff9f7dffffffff9f7dffac88ffffffff9576%
  ff9576ffffffffac88ffffffff9f7dffac88ff9576ff7869ff9576ff9576ff846eff8c72ff6f65ff7367fd6561ff7e6c%
  fd6561ff8c72ff846eff7869ff9f7dff846eff9f7dff9576ffac88ffffffff9f7dffffffffac88ffffffffffffffffff%

>>>>

%% Tue 19 Apr 2016 13:37:03 AEST

@@

\node[gp node center] at (8.574,1.427) {FC Both Runtime (ms)};

@@

  ffffffffac88ff9576ffac88ffac88ffac88ffac88ffac88ff9f7dffac88ffffffffac88ffffffffac88ffffffff9f7d%
  ffffffff9576ff846eff9f7dff9576ffac88ff846eff9576ff7869ff6b63fb605ff7565cf95c5efd6561f95c5ef04757%
  f04557ec4055ea3d54e73952e93c53de2e4ed8264ad9284bd7254ad21f47d62449d01e45d32048d11e46d22047cf1d45%
  d52349cc1b42cf1d44d52349cb1a42cf1d44d11e46d42148d9274bdd2d4ddc2b4cde2d4de53751dc2c4cde2d4dd32148%
  d7254ad52349da294be0304ea00319ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffac88ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7d%
  ffac88ffac88ffac88ff9576ff9f7dff9f7dffac88ff9f7dff9576ff9f7dff9576ffffffff9576ffffffff846eff9f7d%
  ffffffff9576ff846eff846eff9f7dffac88ffffffff9f7dffac88ffffffffac88ffac88ffac88ffac88ffac88ff9f7d%
  ff9f7dffac88ffac88ffac88ffac88ffac88ffffffffffffffac88e1314fffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffffff%
  ff9f7dff9f7dffac88ffac88ff8c72ffac88ffffffff9f7dffac88ff9576ffac88ff9576ff9f7dffac88ffffffff9576%
  ff9f7dffffffff9f7dff9576ff9576ffac88ff7869ff6f65ff8c72ff9f7dff7e6cff846eff7367ff8c72ff9f7dffac88%
  ffac88ff8c72ffac88ff9f7dffac88ff9576ff9f7dffac88ffffffffffffffffffffffffffffffffffffe2324fffffff%
  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffff9f7dffffffffffffff9f7dff9576ffac88ff9f7dffac88ffac88ff9576ffac88ffac88ffffff%
  ff9f7dffac88ffac88ff9f7dffffffff846eff9576ff9f7dff846eff7e6cff7e6cff7367ff846eff7367ff6f65ff6b63%
  ff8c72ff846eff8c72ff7869ffac88ff846eff9576ff9f7dffac88ffffffff9f7dffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88ffac88ffffffffffffffffffffac88ffac88ffffffffac88%
  ffffffff9f7dff9f7dff8c72ffffffff9576ff9f7dffffffffac88ff8c72ffac88ff8c72ff846efd6561fc6260fd6561%
  fa5e5ffa5e5fff7869ff7869ff6f65ff6b63ff9576ff846eff6f65ff7e6cff7e6cff8c72ff9f7dffffffff9f7dffffff%
  ffffffffac88ffffffffffffffffffffffffffffffffffffe73952ffffffffffffffffffffffffffffffffffffffffff%

@@

  ff9f7dff9576ff7869ff9f7dff9f7dffac88ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88%
  ffac88ffffffffac88ffac88ffac88ffac88ff9f7dffac88ff9f7dff8c72ffac88ff846eff7869ff8c72ff7869ff7869%
  f95c5efe6862fc6260f5535bf5535bf5515bf85a5dfa5e5ffa5e5ffb605fff6f65ff7367ff6b63ff7e6cf95c5efc6260%
  ff846eff9576ff9f7dffffffffffffffac88ff9f7dffffffffffffffffffffffffffffffffac88f04557ffffffffffff%
  ffffffffffffffac88ffffffff9f7dffac88ffac88ff9576ffffffffffffffffffffac88ffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffac88ff9576ffffffffac88ff8c72ff7e6cff846eff7869%
  ff9576ff7e6cff846efc6260f95c5efe6862f7565cf7585dfa5e5ff5535bfa5e5ff95c5efa5e5fff6b63ff8c72fa5e5f%
  fe6862f6545cfb605ffd6561ff6b63ffac88ff8c72ffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dff8c72ff9f7dff9f7dff9f7dff9f7dff8c72%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffac88ffac88ff9f7dffffffff8c72%
  ff8c72ff8c72ff6f65ff7367ff6f65ff6f65fb605ffb605ff7565cf7585df85a5dfe6862fa5e5fff6f65f04757fb605f%
  fa5e5ffa5e5ffd6561f5515bfa5e5fff7367fb605ffe6862ff7e6cff9576ff9576ffac88ffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffac88ff846e%
  ffac88ffac88ffffffffffffffac88ff9f7dffac88ffffffffffffffffffffffffffffffffffffff9f7dffffffffffff%
  ffffffff9f7dffac88ff9576ff8c72ff846eff846efb605fff7869ff7367ff7367f5535bfd6561f95c5efd6561f95c5e%
  f85a5df85a5df95c5efb605ffe6862ff6f65fa5e5ff85a5df7565cf85a5dfa5e5ffd6561ff846eff7e6cffac88ffac88%
  ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffffffff8c72ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffac88%
  ffac88ffffffff8c72ff9576ff9576ffffffff8c72ff9576ffffffffffffff8c72ffffffffffffffffffffac88ffffff%
  ffac88ffac88ffffffffffffffac88ffac88ff9f7dffac88ff8c72ff846eff7869ff7e6cff6f65fa5e5ff6545cf7565c%
  f95c5ef7565cf95c5ef7565cf7585dfb605ff5515bff6f65ff7869ffac88ff7367fd6561f24a59fa5e5ffe6862ff6b63%
  ff846eff9576ff9576ff9576ffac88ff9f7dffffffffffffff9576ffffffffac88ffffffffffffffac88ffffffffffff%
  ffffffffffffffac88ffac88ffac88ffac88ffffffffac88ffac88ff9576ffac88ff9576ff9f7dff9576ffac88ffac88%
  ffac88ffac88ffffffffac88ffffffffffffffac88ff8c72ff8c72ffffffff9576ff9576ff7e6cff6f65fe6862fa5e5f%
  ff6b63fa5e5ff7585df5535bf7565cf95c5efc6260f95c5eff7869ff7869ff6b63ff6f65fe6862ff846efe6862ff7869%
  fd6561f85a5dfe6862ff6f65ff8c72ff9576ffac88ffac88ff9f7dffffffffffffff9f7dffac88ffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffff9f7dffffffff9576ff9576ffac88ff9f7dffac88ffffffffac88%
  ff9576ff9576ffac88ffac88ffffffffffffffffffffac88ffffffffffffffac88ffac88ffac88ffac88ff9576ff9576%
  ff7e6cff7e6cfe6862fd6561fa5e5ff34e5af14958f85a5df7565cfc6260ff7869ff6f65fa5e5fff7e6cff7e6cff7e6c%
  ff7e6cff8c72ff9576ff6b63ff8c72fa5e5ffd6561ff6f65ff7869ff846eff9576ffac88ffffffffffffff9f7dffffff%
  ffac88ffffffff9f7dffffffff9f7dff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffac88%
  ffac88ffffffff9f7dffac88ffac88ff9576ffffffff8c72ff9f7dffffffffffffffffffff9f7dffac88ffffffff9f7d%
  ffac88ff9f7dff9576ff9576ff7e6cff6b63ff8c72f6545cf5515bf6545cfa5e5fff6b63f6545cf7565cfb605fff6b63%
  ff846eff7869ff8c72ff8c72ff8c72ff6f65ff7e6cff7367ff7367ff846eff7367ff7367ff7869ffffffff8c72ffac88%
  ffac88ffac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffac88ffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffac88ff9f7dff9576ffffffff9f7dffffffffffffffac88ffac88ff9f7dffffff%
  ff9f7dffac88ffac88ffffffffac88ffac88ff9f7dff9576ff7e6cff7367fc6260ff7367fc6260f95c5ef95c5ef6545c%
  f85a5dfb605fff6f65fb605fff6b63ff7367ff7e6cff7367ffffffff9f7dff6b63ff7869fe6862ff7869ff9f7dff9576%
  ff7e6cff8c72ffffffff8c72ffac88ff9f7dffac88ffac88ffac88ff9f7dff9576ffac88ffffffffffffff9f7dffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dff9f7dffffffffac88ff9f7dffffffff9f7d%
  ffffffff9576ffffffff9f7dffac88ffac88ffac88ff9f7dffac88ff9576ff9576ff9576ff8c72ff7e6cff7367ff6b63%
  f5515bfa5e5ff85a5df6545cf5535bf7565cff7e6cfc6260ff7869ff9f7dff7e6cff9576ff7e6cff8c72ff8c72ff7367%
  ff7367ff7367ffac88ff9f7dff9f7dffac88ffac88ffac88ffac88ff9f7dffac88ff846eff9576ffffffffac88ff9f7d%
  ff8c72ff8c72ffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffac88%
  ff9f7dffac88ffac88ffac88ffac88ff9f7dffac88ffffffff9576ff8c72ffac88ff9f7dffac88ffac88ffffffff846e%
  ff9576ff8c72ff7869ff9576fb605ff5535bfb605ff7585dff6b63fd6561ff7367ff7869ff7869ff846eff9f7dff7e6c%
  ff6f65ff9576ff7367ff8c72fc6260ff7e6cff846eff7e6cff8c72ff9f7dff9576ffffffffac88ffac88ff846eff846e%
  ff6f65ff9576ffac88ffffffffac88ffffffffffffffffffffffffff9f7dffffffff9f7dffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffff9f7dff9f7d%
  ffac88ffac88ffffffff8c72ffac88ffffffffac88ffac88ffffffffac88ffffffff9576ff9f7dffac88ffac88ff9576%
  ff9f7dffac88ff846eff9f7dff9576ff846eff846eff7e6cff6b63fa5e5ffd6561fd6561fd6561fa5e5ffb605fff7869%
  ff9576ff9576ff8c72ff8c72fc6260fd6561fc6260ff846eff7869ff7e6cff7e6cff846effac88ff9f7dff9f7dff9576%
  ffac88ffffffff9f7dff8c72fd6561ff7e6cff846effffffff9576ffac88ff9f7dffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88ffac88ff9f7dff9576ffffff%
  ffffffff9f7dffffffff7e6cff9576ff9576ff9576ffac88ff9f7dff7869ff7869ff9576ff7367fe6862fc6260ff846e%
  fc6260fd6561ff7367ff8c72ff9576ff6f65ff8c72ff9f7dffac88ff6f65fe6862ffac88ff9f7dff7869ff6f65ff7e6c%
  ff9f7dffac88ffffffffac88ffac88ff9f7dffac88ff7869ff7e6cff7e6cff7e6cff9f7dff9576ffac88ff9f7dff9576%
  ffffffff9f7dff9f7dff8c72ffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffffffffffffffac88ff9576ff9576%
  ffac88ff9f7dffac88ffac88ff9f7dffac88ff9f7dff846eff7e6cffac88ff846eff8c72ff8c72ff846eff7869ff6f65%
  ff8c72ff9576ff6f65ff6b63ff6f65ff8c72ff7869ff846eff7e6cff846eff9576ff846eff9576ff9576ff8c72ff7869%
  ff9f7dff9576ff7e6cff9576ff9f7dff9576ffffffffac88ff8c72ffffffffac88ffac88ff9576ff6f65ff7869ff9f7d%
  ff9f7dff8c72ffffffff9f7dff8c72ff9f7dff7e6cf85a5df85a5dffac88ffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffac88ffffffffac88ffac88ff9f7d%
  ffffffff9f7dffac88ffffffffffffffac88ffffffffffffff8c72ff7e6cff846effac88ff9f7dff8c72ff9f7dff9576%
  ff846eff846eff846eff846eff8c72ff846eff9576ff6b63ff6f65ff8c72ff7e6cff6f65ff9576ff8c72ff7e6cff846e%
  ffac88ff846eff9576ff7869ff7e6cff846eff9576ff9f7dff9576ff8c72ffffffffffffffac88ffac88ffac88ffac88%
  ff9576ffac88fe6862ff9576ff9f7dffffffffffffffac88ff9576ff7869ff9f7dfe6862f6545cfe6862ffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffff%
  ffac88ffac88ffffffff9f7dff9f7dffffffffffffffac88ff9f7dffac88ffac88ffac88ffac88ffac88ffffffff9f7d%
  ff8c72ffac88ff8c72ff846eff9f7dff8c72ff7e6cffac88ff9576ff7e6cff7869ff846eff7e6cff7869ff8c72ff6b63%
  ff7e6cff7367ff7869ff846eff9f7dff9576ff9f7dff8c72ff7e6cff9576ffac88ffac88ff9f7dffac88ffffffffffff%
  ff9576ff8c72ff7869ffac88ff9576ffac88ff9576ffac88ffac88ff9f7dffffffff8c72ff7e6cfb605fff7367ff7869%
  f5535bf85a5dff9f7dffffffff9f7dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffac88ffac88ff9f7dffac88ff9576ffffffffac88ffac88ffac88ff9f7dffac88%
  ffac88ff7e6cffffffffffffff7e6cff7e6cff8c72ff7367ff8c72ff7e6cff9576ffac88ff9f7dff8c72ff7e6cff7869%
  ff7869ff7e6cff7869ff7367ff7869ff7e6cff846eff9576ff9576ff846eff9576ff9f7dff9f7dff9576ff9f7dffffff%
  ffffffff9f7dff9f7dff9f7dffac88ffac88ffac88ff8c72ff8c72ff7e6cffac88ff9f7dffac88ff9f7dff9f7dffffff%
  ff9576ff6b63fc6260fd6561ff7367fd6561ff8c72ffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ff9f7dff9576ffffffffffffffffffffffffffffffff9f7dffffffff9f7d%
  ffffffff9f7dff9576ffac88ff846eff9576ff9576ff9f7dffac88ffffffff8c72ff7e6cff9576ff8c72ffac88ff846e%
  ffac88ff9576ff8c72ffac88ff8c72ff7e6cff9f7dff9f7dff9f7dff9f7dff846eff8c72ff9576ff846effffffff9f7d%
  ff9576ff7e6cff9f7dffffffffac88ffffffff9f7dff9f7dffffffff9f7dff9f7dff7e6cff8c72ff846eff9f7dff9576%
  ffffffffffffffac88ffffffffac88ff9576ff6b63fb605fff7869ff7367ff8c72ffac88ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88%
  ffac88ff9f7dffffffff9f7dff9f7dffac88ff9f7dffffffffac88ffac88ffac88ffac88ff9f7dffffffff846eff7869%
  ff6f65ff846eff8c72ff9576ff7e6cff7e6cff9576ff9576ff8c72ff8c72ff8c72ff9576ff9576ffac88ffac88ff846e%
  ff8c72ff9f7dffac88ff9576ff846effac88ff8c72ffffffffac88ffac88ffac88ffffffffffffffffffffac88ffffff%
  ff8c72ff8c72ffffffffac88ffac88ff9f7dff9f7dffffffffac88ffffffff8c72ff9576ff7869ff8c72ffac88ffac88%
  ff9f7dff9f7dffffffffac88ffffffffffffffffffff9f7dff8c72ff8c72ff9576ffac88ff8c72ffac88ffffffffac88%
  ff9f7dff9f7dff9576ffac88ffffffff7869ff9576ff846eff7869ff9576ff7367ff846eff9f7dff9f7dff8c72ffac88%
  ff9f7dff7869ff9576ff846eff9576ffffffffac88ff9576ff9f7dff9576ffac88ff9f7dffffffffffffffac88ffac88%
  ffffffffffffffffffff9f7dffac88ff9f7dff8c72ff9576ff9f7dff9f7dffffffffac88ff9f7dffffffffffffffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffff9576ff9f7dff9576ffac88ff9576%
  ffac88ffac88ff9f7dff9576ffac88ff846effac88ffac88ff9f7dffac88ff8c72ff9f7dff846eff8c72ff8c72ff9f7d%
  ffac88ffac88ff8c72ffac88ff8c72ff9576ff846eff9f7dff9576ff9576ff9576ffffffff8c72ffffffff9576ffffff%
  ffffffff9576ff9f7dffac88ffffffff9f7dffffffff9f7dff7e6cff9576ff9576ff9f7dffffffffac88ffac88ffac88%
  ff9576ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffac88ffffffffffffffffffffffffffffff%
  ff9f7dff9f7dffac88ffac88ff9f7dffac88ffac88ffffffffac88ffffffffffffffffffff9f7dff9f7dffffffff8c72%
  ffac88ffffffff9f7dff9f7dffffffff9f7dff9f7dffac88ff9f7dffac88ff846eff9576ff7e6cff846eff9576ff7e6c%
  ff846eff8c72ff8c72ff9f7dff8c72ffac88ffac88ffac88ffac88ffffffff9576ff9576ffac88ffac88ff846effffff%
  ff9576ffffffffac88ffac88ffac88ffffffffffffff9f7dff9f7dffffffff9f7dffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ffac88ff9f7dff8c72ff7e6cff8c72ff9576ff9576ff8c72ffffffffac88ff9f7dffffff%
  ff9f7dffffffffffffff9f7dffffffffffffff9f7dff8c72ff846eff9f7dffac88ffac88ff9576ff7869ffac88ff7e6c%
  ff9576ff9f7dff9576ff8c72ff7e6cff846eff7869ff6b63ff846eff8c72ff8c72ffffffffffffffac88ff9f7dff9f7d%
  ffffffff9f7dffac88ff9f7dffac88ffac88ffac88ff9576ffffffffac88ffffffffac88ffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffac88ff9f7dffffffffac88ff9f7dff9f7dff8c72ff7367ffac88ff846eff8c72ffac88%
  ffac88ffffffff9f7dffac88ff9f7dffffffffac88ffffffff9576ffac88ff9f7dff9f7dffffffffac88ffac88ff9f7d%
  ffac88ffffffff846eff9576ff9f7dff8c72ff7367ff7367ff7367ff7869fa5e5ffe6862f7585dff6f65ff846eff9576%
  ffac88ffac88ff8c72ffac88ffffffffac88ff9f7dff9f7dffffffff9576ffac88ffac88ff8c72ff9f7dffac88ffac88%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dff8c72ff7e6c%
  ff7e6cff8c72ff7e6cff9576ff846eff9f7dff9f7dff9f7dffffffffffffffac88ffffffffac88ff9576ffffffff9576%
  ffffffff9576ffac88ff9f7dffac88ff9576ff846eff7e6cff846eff6b63ff7367f7585df6545cfc6260f7585df7565c%
  fb605ff95c5efe6862ff8c72ff9f7dffac88ffac88ffac88ff9f7dff9f7dffac88ff9576ffac88ff8c72ffffffff9f7d%
  ffffffff9576ff9f7dffffffffac88ffac88ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%

@@

  ffac88ff9f7dff8c72ff8c72ff846eff846eff8c72ff846eff8c72ff9f7dffac88ffac88ffac88ffac88ffac88ffffff%
  ff9f7dffac88ffffffffac88ff8c72ff7e6cff846effac88ff8c72ff7e6cff7869ff7367fe6862ff6b63fe6862fa5e5f%
  f7565cf24a59f34d59f5535bf14958f4505af7565cff6f65ff846eff9576ffffffffffffffac88ffac88ffac88ff9576%
  ff8c72ff9f7dff9f7dff9576ffac88ffffffff8c72ffffffffffffffffffffac88ffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dff9576ff9f7dff8c72ff846eff9576ffac88ffffff%
  ffffffffffffffffffffac88ffac88ff9f7dff8c72ff9f7dff9576ff9f7dff7869fe6862ff7e6cff9576fd6561ff7e6c%
  ff6f65fb605ffd6561f7565cfd6561f85a5df24b59fa5e5ffa5e5ff34d59f7585df4505afb605fff846effac88ff9f7d%
  ff9576ffac88ffac88ffac88ffffffff9f7dff846eff8c72ff9f7dffffffffac88ff9f7dffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ff9f7dff9f7d%
  ffffffffac88ffac88ffac88ffac88ffac88ffffffffac88ff9f7dffffffff846effac88ff7869ff846eff7e6cff8c72%
  ff6b63fd6561ff846efe6862f95c5efc6260ff7869fa5e5ffb605ff34e5af5535bf5515bff6b63f4505af85a5df5535b%
  ff6b63ff7367ff8c72ff9f7dff9f7dffffffffffffffffffff9f7dff9f7dff846eff8c72ffffffff9f7dff9f7dff9f7d%
  ff9576ffac88ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffff%
  ffac88ffac88ffffffff9f7dff9576ffac88ffffffffac88ffffffffffffffac88ffffffff9f7dff9f7dff9f7dff8c72%
  ffac88ff9576ff7e6cff7367ff6b63f5515bfa5e5ffd6561f6545cfe6862fe6862ff6b63f85a5dfd6561f5515bf6545c%
  fb605ffb605ff7585df85a5df7565cfc6260fe6862ff8c72ff9576ff9f7dffffffffffffff9f7dffffffffac88ff9f7d%
  ff8c72ffffffffffffff9f7dffffffffffffff9576ffffffffffffffac88ffac88ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dffac88ffffffffac88ffac88ffffffffac88ffffffffac88ff9f7dffffffffffff%
  ffffffffac88ffffffff9576ff9576ff8c72ff7367fa5e5ffc6260f95c5ef95c5ef95c5ef6545cf7585dff7367fd6561%
  f7585dfd6561ff6b63fe6862fc6260f5535bff6f65fd6561ff7869ff8c72ff846eff9576ff9576ff9f7dff8c72ff9f7d%
  ff9f7dff9f7dffac88ffac88ffac88ffffffff9f7dffac88ffac88ffffffff9f7dffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ff9f7dffffffffac88ffffffffffffff9f7dffac88ff9f7dffffff%
  ffac88ffffffffffffffffffff9f7dff9576ff9f7dff9576ff846eff846efd6561ff6b63f7565cf5515bf14958f85a5d%
  fa5e5ffb605fff7367fc6260ff846eff7869fb605ffd6561fb605ffe6862fc6260ff7869ff6b63f85a5dfe6862ff7869%
  ffac88ffac88ffffffff9f7dff8c72ffac88ffac88ffffffffac88ffffffff9f7dffac88ffffffffffffffac88ff9f7d%
  ffffffffac88ffffffffffffffffffffac88ffac88ff9f7dffffffffac88ffac88ff8c72ff7e6cff6f65ff6b63ff6b63%
  f6545cfa5e5ff14858f7565cfb605ff85a5dff7367ff7367ff6f65ff6f65ff9f7dff7869ff7367ff7367fd6561fc6260%
  fe6862fc6260fe6862ff7e6cff9576ff9f7dffac88ffffffffac88ffffffff846effac88ffffffff9576ff8c72ff9f7d%
  ffffffffffffff9576ffffffffac88ff9f7dffffffff9f7dffffffffac88ffac88ffffffff9f7dff9576ff9f7dff9f7d%
  ff9576ff846eff7367f4505afc6260f5535bf7585df4505af5515bf7585dfe6862ff7869ff7e6cff8c72ff846eff9576%
  ff8c72ff7869fc6260fe6862f7585dfb605fff6b63ff7367ff7367ff8c72ffac88ff9576ffffffff9f7dffac88ff8c72%
  ffac88ff8c72fe6862ff7869ff846effac88ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffff9f7dffffffffac88ffffffffffffffffffffffffffffffff9576ffffffffffffffffffff9576ffffffff9f7d%
  ffac88ff9576ff7e6cff9576ff846eff7367ff6f65ff6b63f95c5efb605ff4505af7585dfb605ffb605fff7367fd6561%
  ff7367ff8c72ff9576ff9f7dff9576ff7367ff7367ff7e6cf7585dff6f65ff7367ff9576ff9f7dff846eff8c72ff846e%
  ff7869ff9576ff9f7dff8c72ff9f7dff7869f95c5eed4155f85a5dff846effac88ff9f7dffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffffffff9f7dffffff%
  ff9f7dffac88ffac88ffac88ffac88ffffffff9f7dff9576ff846eff9576ff7e6cff7869ff846eff6f65ff6b63fa5e5f%
  ff6f65ff846eff7e6cff7869ff7e6cff9f7dff9f7dff8c72ff9576ff7367ff846eff7869ff7869ff846eff7e6cff9576%
  ffac88ff8c72ff6b63ff7869ff7e6cfd6561ff7e6cff8c72ff9576ff9576fb605feb3e54ee4156fd6561ffffffffffff%
  ffac88ffffffff9f7dffffffff8c72ffac88ffac88ffffffffffffff8c72ff8c72ff8c72ff8c72ff8c72ff8c72ff846e%
  ff7367ff6f65ff7869fd6561ff6f65ff7869ff8c72ffac88ff7e6cffac88ff9576ff9f7dff8c72ff8c72ff9576ff846e%
  ff7869ff7e6cff8c72ff8c72ff9f7dff8c72ffffffff7e6cfe6862fc6260ff7869ff846effac88ff7869ff9f7df5535b%
  f85a5dff6f65ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffff%
  ffffffffffffffffffffac88ff9f7dffac88ffac88ffffffffffffffac88ffac88ff9f7dffffffffffffff9f7dff9576%
  ff8c72ff6f65ff7869ff6f65ff8c72ff7e6cff846eff7367ff7367ff7e6cff7e6cff9f7dff9576ff9f7dff9576ffac88%
  ff8c72ff9576ffffffffffffff846effffffff8c72ffac88ff7e6cff8c72ffac88ff9576ff7e6cfd6561fe6862ff7367%
  ff7367ff9f7dff9576ff846eff8c72ff7869ffac88ff9f7dffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffff9f7dffffffffffffffac88ffac88ff9576ffffffffffffff9f7dffffffff9f7dffffff%
  ffffffff9f7dffac88ffac88ff9576ff9576ff7e6cff6f65fe6862ff846eff846eff9576ff7869ff9576ff846eff8c72%
  ff7e6cff8c72ff7869ff846eff7367ff9576ff9f7dff9576ff9f7dffac88ff8c72ff7869ff9f7dff7e6cff9576ff9f7d%
  ff8c72ff6b63ff7869ff9f7dff846effac88ff8c72ff9f7dff9f7dff9f7dffac88ffac88ffffffffffffffffffffffff%
  ffac88ffffffffffffffffffffffffffffffff846effffffff9f7dffac88ff9576ff846eff9576ff7367ff7869ff8c72%
  ffac88ff8c72ff9f7dff9576ff8c72ff9f7dff7e6cfd6561ff7869ff8c72ff846eff846eff9576ff9f7dffac88ffffff%
  ff9576ff9f7dffffffffac88ff8c72ff9576ff9f7dff7e6cffac88ff7869ff9f7dffac88ffac88ff9f7dffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88%
  ffffffff9f7dffac88ffac88ff9576ffac88ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffac88ff8c72%
  ff9f7dff846eff9576ff9576ff9576ff8c72ffac88ff9576ff9f7dff8c72ff8c72ff846eff8c72ff9f7dff846eff9f7d%
  ff9576ffffffff7869ff9f7dffac88ff9f7dff7e6cff9f7dff9f7dff6b63ff9576ff9576ffffffff9f7dffffffff9576%
  ff9f7dff8c72ffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffff9576ff9576ff9576ff8c72ffac88ffac88ff9576ffffffff8c72%
  ff9576ff8c72ffffffff9f7dff8c72ff9576ff9576ff9f7dffac88ff9576ff9f7dff9f7dff9f7dff6f65ff846eff9f7d%
  ff9f7dff9576ff9f7dffffffffac88ff9576ff9576ffffffffffffffac88ff9f7dff7869ff846eff846eff9576ff846e%
  ffffffff8c72ff9f7dff9576ffac88ffffffffac88ffffffffffffffffffffac88ffac88ffffffffffffffffffffffff%
